Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-19 documents/mixtures/mixture_models.tex
figure caption for dstn

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{mixtures_vs_K_exp.png}%
\includegraphics[width=\figurewidth]{mixtures_vs_K_dev.png}\\
\includegraphics[width=\figurewidth]{mixtures_vs_K_lux.png}%
\includegraphics[width=\figurewidth]{mixtures_vs_K_luv.png}
\caption{Comparisons of approximations.  \textsl{top-left:} The
  dependence of amplitude $a^{\exp}_m$ and root-variance
  $\sqrt{v^{\exp}_m}$ on $M^{\exp}$ for the exp profile.
  \textsl{top-right:} The same but for the dev profile.
  \textsl{bottom-left:} The same but for the lux profile.
  \textsl{bottom-right:} The same but for the luv profile.}
\end{figure}

>>>>

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{mixtures_vs_K_exp.png}%
\includegraphics[width=\figurewidth]{mixtures_vs_K_dev.png}\\
\includegraphics[width=\figurewidth]{mixtures_vs_K_lux.png}%
\includegraphics[width=\figurewidth]{mixtures_vs_K_luv.png}
\caption{Comparisons of approximations.  \textsl{top-left:} The
  dependence of amplitude $a^{\exp}_m$ and root-variance
  $\sqrt{v^{\exp}_m}$ on $M^{\exp}$ for the exp profile.
  \textsl{top-right:} The same but for the dev profile.
  \textsl{bottom-left:} The same but for the lux profile.
  \textsl{bottom-right:} The same but for the luv profile.\label{fig:M}}
\end{figure}

\clearpage
\begin{figure}
% DSTN:  This should be a 3-across by 2-down figure,
\caption{Demonstration of use of the profiles, or the implicit
  generative model in this \documentname.  \textsl{top-left:} The
  circular dimensionless $M^{\luv}=8$ mixture-of-Gaussian
  approximation to the luv profile, represented on a very fine pixel
  grid. \textsl{top-middle:} The ellipse representing the non-trivial
  affine transformation to be applied to the circular, dimensionless
  profile.  \textsl{top-right:} The sheared profile.
  \textsl{bottom-left:} A $K=3$ mixture-of-Gaussian model of the
  pixel-convolved point-spread function, represented on the very fine
  pixel grid.  \textsl{bottom-middle:} The sheared profile convolved
  with the PSF, represented on the very fine pixel grid.
  \textsl{bottom-right:} The sheared luv convolved with the PSF, but
  now shown on a realistic pixel grid.  Because by assumption the PSF
  is a pixel-convolved PSF, the representation on the realistic grid
  is found simply by interpolating the convolved high-resolution
  model.\label{fig:example}}
\end{figure}
